Proposed Solution

### 2016-01-29 system.tex
autocommit

Before describing how our system for learning rules works, we first outline a translator which converts configuration files into an intermediary representation. Typing is based on an
already given set of basic types. However, typing is also a system module than can be easily extended to support
more types. In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.

@@

Each line of a configuration files can be reduced to a keyword value pair
In the parsing step we collect all lines in the file into a set of such pairs $(k, v)$, where $k$ denotes 
variable name and $v$ denotes variable value. 
However, based only on a single example value of $v$ we cannot fully determine the type of $k$.
We instead assign a distribution of type to a value, an idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.

>>>>

To learn rules, we first translate to the intermediate representation where each line of a configuration file is reduced to a keyword-value pair $(k,v)$.
Of course, parsing is language dependant and users may provide extra help to the translator for their specific language, such as specifying a comment character.
We must assign types to the keywords to guide the learning modules.
With typed keyword-value pairs, we can run each learning module independent of each other.
We learn a set of rules over a every file, then merge the rules of all files based on some user definied measure of consistency.
The final rule set is all the rules that are true on the learning set

@@

However, based only on a single example value of $v$ we cannot fully determine the type of $k$.
We instead assign a distribution of type to a value, an idea is closely related to existentially quantified types \cite{Launchbury93lazyfunctional}.
However, typing is also a system module than can be easily extended to support more types. 
In that case the user will need to provide rules for type inference and probability distributions for values where type inference is ambiguous.
